---
title: ""
format:
  html:
    toc: false
    page-layout: full
    css: styles.css
    theme: default
output-dir: docs
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tibble)
library(glue)

# Communities
communities <- tribble(
  ~short,   ~name,                                      ~subtitle,                             ~file,        ~status,
  "CPDFN",  "Chipewyan Prairie Dene First Nation",       "Community camera monitoring results", "CPDFN.html",  "Available",
  "OMGD19", "Otipemisiwak Métis Government District 19", "Community camera monitoring results", "OMGD19.html", "Available",
  "BLMS",   "Beaver Lake Métis Settlement",              "Community camera monitoring results", "BLMS.html",   "Available",
  "GLMS",   "Gift Lake Métis Settlement",                "Community camera monitoring results", "GLMS.html",   "Coming Soon",
  "BLCN",   "Beaver Lake Cree Nation",                   "Community camera monitoring results", "BLCN.html",   "Coming Soon",
  "CONK",   "Conklin Métis",                             "Community camera monitoring results", "CONK.html",   "Coming Soon"
)

```

::: {.cbm-hero}
::: {.cbm-hero-inner}

# Community-Based Monitoring & Engagement Online Reports

We work collaboratively with communities throughout Alberta on projects driven by community interests and objectives.

<div class="cbm-hero-actions"> <a class="cbm-btn cbm-btn-primary" href="#reports">Browse reports</a> <a class="cbm-btn cbm-btn-ghost" href="#about">About this portal</a> </div>

:::

:::

## Reports {#reports}

```{r, echo=FALSE}

out <- "<div class='cbm-grid'>\n"

for (i in seq_len(nrow(communities))) {

  short    <- communities$short[[i]]
  name     <- communities$name[[i]]
  subtitle <- communities$subtitle[[i]]
  file     <- communities$file[[i]]
  status   <- communities$status[[i]]

  status_class <- if (status == "Coming Soon") "cbm-status status-coming" else "cbm-status"

  button_html <- if (status == "Coming Soon") {
    "<span class='cbm-btn cbm-btn-disabled'>Coming Soon</span>"
  } else {
    glue("<a class='cbm-btn cbm-btn-primary' href='{file}'>Open report →</a>")
  }

  out <- paste0(
    out,
    glue::glue("
<div class='cbm-card'>
  <div class='cbm-card-top'>
    <div class='cbm-badge'>{short}</div>
    <div class='{status_class}'>{status}</div>
  </div>

  <h3 class='cbm-card-title'>{name}</h3>
  <p class='cbm-card-subtitle'>{subtitle}</p>

  <div class='cbm-card-actions'>
    {button_html}
  </div>
</div>
"),
    "\n"
  )
}

out <- paste0(out, "</div>\n")

knitr::asis_output(out)

```

## About this portal {#about}

This site is a hub for community-facing monitoring outputs (HTML reports) that live in the same docs/ folder used for GitHub Pages.

::: {.cbm-footer}
::: {.cbm-footer-grid}

::: {.cbm-footer-block}

### Contact

For questions about these reports or to request updates, contact the ABMI Community-Based Monitoring & Engagement team.
:::

::: {.cbm-footer-block}

### Acknowledgement

This work is made possible through reciprocal relationships with partner communities and stewardship on Indigenous territories across Alberta.
:::

:::
:::
